% Preamble
\documentclass[11pt]{PyRollDocs}
\usepackage{textcomp}

\addbibresource{refs.bib}

% Document
\begin{document}

    \title{The Marini Spreading PyRoll Plugin}
    \author{Christoph Renzing}
    \date{\today}

    \maketitle

    This plugin provides a spreading modelling approach with Marini's formula for flat rolling, adapted on groove rolling by an equivalent rectangle approach.


    \section{Model approach}\label{sec:model-approach}

    \subsection{Marini's spread equation}\label{subsec:marinis's-spread-equation}

    \textcite{Marini1941} proposed \autoref{eq:marini} for estimation of spreading in flat rolling.
    Where $h$ and $b$ are height and width of the workpiece with the indices 0 and 1 denoting the incoming respectively the outgoing profile.
    $A$ and $B$ are parameters introduced by Marini.
    $R$ is the roll radius and $\mu$ is the friction coefficient.


    \begin{equation}
        A = \frac{\sqrt{\Delta h}}{2 \mu \sqrt{R}}
        \label{eq:marini-parameter-a}
    \end{equation}

    \begin{equation}
        B = \sqrt{\frac{\Delta h}{R}}
        \label{eq:marini-parameter-b}
    \end{equation}

    \begin{equation}
        b_1 = b_0 + \frac{2 \Delta h b_0 \left( R - \frac{h_0}{2} \right) B }{h_1 b_0 + \left( \frac{b_0 \left( h_0 + h_1 \right)}{2} \frac{1 + A}{1 - A} \right) \frac{0.91 \left( b_0 + 3 h_0 \right)}{4 h_0} + 2 h_1 R B}
        \label{eq:marini}
    \end{equation}


    \section{Usage instructions}\label{sec:usage-instructions}

    The plugin can be loaded under the name \texttt{pyroll\_marini\_spreading}.

    An implementation of the \lstinline{width} hook on \lstinline{RollPass} is provided,
    calculating the spread using the equivalent rectangle approach and Marini's model.

    Several additional hooks on \lstinline{RollPass} are defined, which are used in spread calculation, as listed in \autoref{tab:hookspecs}.
    Base implementations of them are provided, so it should work out of the box.
    For \lstinline{marini_parameter_a} and \lstinline{marini_parameter_b} the equations~\ref{eq:marini-parameter-a} and~\ref{eq:marini-parameter-b} are implemented.
    Friction coefficient can be adjusted individually.
    Provide your own hook implementations or set attributes on the \lstinline{RollPass} instances to alter the spreading behavior.

    \begin{table}
        \centering
        \caption{Hooks specified by this plugin. Symbols as in \autoref{eq:marini}.}
        \label{tab:hookspecs}
        \begin{tabular}{ll}
            \toprule
            Hook name                     & Meaning                                      \\
            \midrule
            \texttt{marini\_parameter\_a}   & Parameter $A$ of Marini's spreading equation \\
            \texttt{marini\_parameter\_b}   & Parameter $B$ of Marini's spreading equation \\
            \texttt{friction\_coefficient} & Friction coefficient $\mu$                   \\
            \bottomrule
        \end{tabular}
    \end{table}

    \printbibliography

\end{document}